MLH1 Results Outline

### 2020-02-22 doc/Results.rmd
fixed some erroneus p values in Q1 SC section

Comparing the means of single bivalents is complicated by the fact we can't identify the chromosome identitied the physical size (in terms of SC-AE) is the closet approximation we can make.

@@

For this reason we use a reduced bivalent data set made up of chromsomes (below the 2nd quartile for SC length of single cells). A total of `r sum(Q1.real.short_mouse_table$n_obs)` 'short' bivalents were isolated from `r sum(Q1.real.short_mouse_table$ncells)` oocytes and spermatocytes.

Even though this smaller data set has decreased power due to redcued sample size, ...

@@

For all but one strain, _musculus^SKIVE^_, the mouse mean for the short bivalents are significantly longer <how much longer, the largest difference across sexes by strain are>  (t.test; p = `r Q1_mus.av_shortSC_t.test.WSB$p.value`, `r format(Q1_mus.av_shortSC_t.test.G$p.value, scientific = F)`, and `r format(Q1_mus.av_shortSC_t.test.LEW$p.value, scientific = F)`
for _domesticus^WSB^_, _domesticus^G^_ and _domesticus^LEW^_ respectively.
and (t.test; p= `r format(Q1_mus.av_shortSC_t.test.PWD$p.value, scientific = F)`, `r Q1_mus.av_shortSC_t.test.KAZ$p.value`, and `r  format(Q1_mus.av_shortSC_t.test.SKIVE$p.value, scientific = F)` for _musculus^PWD^_ , _musculus^KAZ^_ , _musculus^SKIVE^_  respectively.

@@

These results indicate that there are strain specific effects for the SC-AE area --

the large G strain effect is likely driven by the high female mean total SC area

sex is the next strongest (most significant) effect.

For the short bivalent data -- run through the same models...

@@

From this (M2) model sex effect, male is most significant (glm; p =`r summ.Q1.glm_short.SC_M2$coefficients[,4][10]`). while the skive strain effect (glm; p=`r summ.Q1.glm_short.SC_M2$coefficients[,4][8]`) and and SKIVE*male (glm; p =`r summ.Q1.glm_short.SC_M2$coefficients[,4][16]`) are slightly significant.

In the M2 model, the Sex effect (male) is the only significant p value from this model (glm; p= `r summ.Q1.glm_short.SC_M3$coefficients[,4][10]`).
<should apply caution to the short bivalent dataset> The significant SKIVE effect is driven by  2 of the 4 female skive mice -- having much shorter bivalents comapred to the other female musc strain means.

>>>>

<Comparing the means of single bivalents is complicated by the fact we can't identify the chromosome identitied the physical size (in terms of SC-AE) is the closet approximation we can make.>

@@

We use a reduced bivalent data set made up of chromsomes (below the 2nd quartile for SC length of single cells) to make single bivalent groups which exclude the XX homologs from the female data. A total of `r sum(Q1.real.short_mouse_table$n_obs)` 'short' bivalents were isolated from `r sum(Q1.real.short_mouse_table$ncells)` oocytes and spermatocytes.

<Even though this smaller data set has decreased power due to redcued sample size, it offers a mors comparable set of SC-AE meterics across the sexes>

@@

For all but one strain, _musculus^SKIVE^_, the mouse mean for the short bivalents are significantly longer <how much longer, the largest difference across sexes by strain are>  (t.test; p = `r Q1_mus.av_shortSC_t.test.WSB$p.value`, p =`r format(Q1_mus.av_shortSC_t.test.G$p.value, scientific = F)`, and p=`r format(Q1_mus.av_shortSC_t.test.LEW$p.value, scientific = F)`
for _domesticus^WSB^_, _domesticus^G^_ and _domesticus^LEW^_ respectively.
This pattern is also true for the musculus strins (t.test; p= `r format(Q1_mus.av_shortSC_t.test.PWD$p.value, scientific = F)`, `r Q1_mus.av_shortSC_t.test.KAZ$p.value`, and `r  format(Q1_mus.av_shortSC_t.test.SKIVE$p.value, scientific = F)` for _musculus^PWD^_ , _musculus^KAZ^_ , _musculus^SKIVE^_  respectively.

@@

@@

From this (M2) model sex effect, male is most significant (glm; p =`r summ.Q1.glm_short.SC_M2$coefficients[,4][8]`).

while the skive strain effect (glm; p=`r summ.Q1.glm_short.SC_M2$coefficients[,4][7]`) and and SKIVE*male (glm; p =`r summ.Q1.glm_short.SC_M2$coefficients[,4][16]`) are slightly significant.

In the M2 model, the Sex effect (male) is the only significant p value from this model (glm; p= `r summ.Q1.glm_short.SC_M3$coefficients[,4][14]`).
